FocalGstar

### 2017-06-15 analysis.Rmd
improved raster colors

ZOOM_WMATRIX_SIZE <- 11
FOCAL_MATRIX_SIZE <- 41
MAX_AGGREG_LEVEL <- 8
ZOOMLEVEL <- 3
```

@@

Rendering the aggregated rasters:
```{r rawdata, cache=TRUE, fig.width=5, fig.height=5}
op <- par(mar = rep(0, 4))
for (i in seq_along(rast)) {
  plot(rast[[i]], xlab = NA, ylab = NA,
       legend = FALSE, axes = FALSE, box = FALSE)
}
par(op)
```
## Demo: Variable resolution (zoom)

@@

Now, we want to generate plain images out of the G* rasters:
```{r raw-zoom-gstar, echo=FALSE, cache=TRUE, fig.width=4, fig.height=4}
op <- par(mar = rep(0, 4))
for (g in zoom_gstar) {
  plot(g, xlab = NA, ylab = NA,
       legend = FALSE, axes = FALSE, box = FALSE)
}
par(op)
```

@@

Now, we want to generate plain images out of the Focal G* rasters:
```{r raw-zoom-focalgstar, echo=FALSE, cache=TRUE, fig.width=4, fig.height=4}
op <- par(mar = rep(0, 4))
for (g in zoom_focalgstar) {
  plot(g, xlab = NA, ylab = NA, legend = FALSE, axes = FALSE, box = FALSE)
}
par(op)
```

>>>>

ZOOM_WMATRIX_SIZE <- 11
FOCAL_MATRIX_SIZE <- 41
MAX_AGGREG_LEVEL <- 8
ZOOMLEVEL <- 3
COLORMAP <- interpolate_colortable(
  howmany = 100, "black", "blue", "yellow", "red")

@@

Rendering the aggregated rasters:
```{r rawdata, cache=TRUE, fig.width=5, fig.height=5}
op <- par(mar = rep(0, 4))
for (i in seq_along(rast)) {
  plot(log(rast[[i]]), xlab = NA, ylab = NA,
       legend = FALSE, axes = FALSE, box = FALSE,
       col = COLORMAP, colNA = "black")
}
par(op)
```
## Demo: Variable resolution (zoom)

@@

Now, we want to generate plain images out of the G* rasters:
```{r raw-zoom-gstar, echo=FALSE, cache=TRUE, fig.width=4, fig.height=4}
op <- par(mar = rep(0, 4))
for (g in zoom_gstar) {
  plot(g, xlab = NA, ylab = NA,
       legend = FALSE, axes = FALSE, box = FALSE, col = COLORMAP, colNA = "black")
}
par(op)
```

@@

Now, we want to generate plain images out of the Focal G* rasters:
```{r raw-zoom-focalgstar, echo=FALSE, cache=TRUE, fig.width=4, fig.height=4}
op <- par(mar = rep(0, 4))
for (g in zoom_focalgstar) {
  plot(g, xlab = NA, ylab = NA, legend = FALSE, axes = FALSE, box = FALSE,
       col = COLORMAP, colNA = "black")
}
par(op)
```
